Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2023-01-20 analysis/paper/paper.qmd
update

```{r}
#| label: fig-corr-analysis
#| fig-cap: "A: xxx. B. xxx. C. xxx"
#| fig-width:   7
#| fig-height:  9

@@

@@

library(cowplot)
plot_grid(plot_grid(
          plot_grid(p2_corr_plot, 
                    p3_corr_plot,
                    ncol = 1,
                    labels = c("A", "B")),
          compare_p2_and_p3_correlations_plot,
          ncol = 2,
          labels = c("", "C"),
          rel_heights = c(1, 1.5)),
          correlations_by_raw_material,
          correlations_by_site,
          ncol = 1,
          labels = c("", "D", "E"))

@@

<!-- BM: overall I think the CV values are really not that interesting or informative. They are difficult to interpret because they all cluster around 15-30, which seems to me to be the midpoint between 'highly standardised' (3-5) and 'highly different' (40-50). So I think we will struggle to convince any readers that we have any strong signals of cultural transmission biases in the CV data. Probably we can satisfy most readers that guided variation is the main bias in these data. That's my perspective after reading this paper several times, and re-reading several related papers by Bettiner and Eerkens and Lipo, and others  -->

>>>>

@fig-corr-analysis

```{r}
#| label: fig-corr-analysis
#| fig-cap: "Correlation analysis by chronological phases. A: xxx. B. xxx. C. xxx"
#| fig-width: 7
#| fig-height: 3

@@

plot_grid(plot_grid(
          plot_grid(p2_corr_plot, 
                    p3_corr_plot,
                    ncol = 1,
                    labels = c("A", "B")),
          compare_p2_and_p3_correlations_plot,
          ncol = 2,
          labels = c("", "C"),
          rel_heights = c(1, 1.5)))

@fig-corr-raw-ass

```{r}
#| label: fig-corr-raw-ass
#| fig-cap: A. sth sth B. sth sth.

#| fig-width:7
#| fig-height:5

@@

library(cowplot)
plot_grid(correlations_by_raw_material,
          correlations_by_site,
                    ncol = 1,
                    labels = c("A", "B"))

@@

<!-- BM: overall I think the CV values are really not that interesting or informative. They are difficult to interpret because they all cluster around 15-30, which seems to me to be the midpoint between 'highly standardized' (3-5) and 'highly different' (40-50). So I think we will struggle to convince any readers that we have any strong signals of cultural transmission biases in the CV data. Probably we can satisfy most readers that guided variation is the main bias in these data. That's my perspective after reading this paper several times, and re-reading several related papers by Bettiner and Eerkens and Lipo, and others  -->
